---
title: "index.Rmd"
author: "Eric Large"
date: "2/16/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../source/analysis.r")
library(tidyverse)
```

## Assignment 3

### Introduction: Analyzing Black Incarceration Rates

This analysis focuses on the incarceration rates of Black people in the United
States, who have faced systemic racism and institutional oppression since the 
formation of the country. With racism being one of the most prominent social
issues over the last 200 years, we have seen a plethora of examples in which Black
Americans are targeted unjustly. Whether it be the Jim Crow laws of the past,
police brutality, or the ongoing War on Drugs, it is clear that BIPOC individuals
in the U.S. do not have the same privileges the rest of the population has. As a 
result, I narrowed down my analysis on incarceration rates to focus on five unique
statistics: 1) the county with the highest population of incarcerated Black
people in prison (black_prison_pop), 2) the ratio of incarcerated Black people 
(black_prison_pop) to the total incarcerated population in prison (total_prison_
pop) in this (Los Angeles) county, 3) the ratio of Black prison admissions 
(black_prison_adm) to total prison admissions (total_prison_adm) in Los Angeles 
County, 4) the average admission numbers of incarcerated Black people in prison 
(black_prison_adm) across all counties since 1970, and finally 5) the average
yearly admissions for Black and White males across all counties.

### Summary Information

1) Los Angeles County.
2) ~37% of all prisoners in LA County were Black as of 2016.
3) ~32% of all admitted prisoners in LA county were Black as of 2016.
4) *See `yearly_black_avg_adm` data frame.
5) *See Chart1.

## Trends Over Time Chart

Description: The purpose of this line graph visualization is to highlight the
difference between Black and White male admissions into prison, across all U.S.
counties since data collection from the Vera Institute began in 1970. This data
averages the number of admissions across all counties for each year. Furthermore,
this visual points out how Black males in the U.S. have been targets for unjust
arrest and prison time for decades.

```{r chart1, echo=FALSE}
plot(chart1)
```

## Variable Comparison Chart

Description: This scatter plot demonstrates the high Black population in the U.S.
prison system, that grows almost linearly to the total prison population. Once
again, the aim of this visual is to point out the discrepancy between Black
incarceration rates against the total prison population.

```{r chart2, echo=FALSE}
plot(chart2)
```

## Map

Description: This mapping of the United States looks at the average imprisoned
Black population in each state as of 2016. Moreover, the year 2016 is highlighted
because it is the most recent year with data on `black_prison_pop`. The states
colored in gray represent states without any data on the variable. However, this
visual is still useful as it sheds light on real-world data trends across the 
country. Looking at the legend, the darker shades of red represent states with
a greater imprisoned Black population, while the lighter red/white shaded states
have fewer imprisoned Black people.

```{r map, echo=FALSE}
plot(map)
```